\vspace{-.2in} Squint: Lossy Hierarchical Compression on Symbol Streams \vspace{-.1in}

### 2012-12-12 tex/paper.tex
messing with results

It is useful to look at how the algorithms function on a small piece of data
with both plenty of hierarchical structure, and also some messiness that most
lossless compression schemes would not deal well with. Take the string below,
similar to what one might come across in a math puzzle book.

@@

For most of our benchmark tests, we focused on two extreme kinds of data: one
with large amounts of repetition at all levels, and one with a word and
sentence level structure but with little obvious large-scale repetition.  One
set of test data was constructed by repeating the same letter `a' n-times but
then adding some texture to the data by changing 1/30 of the characters
uniformly at random to `*'. Call these test-cases \emph{rep-n} Another set of
test data was constructed from the first n characters of the book of Genesis
from the KJV version of the Bible.  Call these test-cases \emph{gen-n}

For our first suite of tests, we compare the effectiveness of the
\Similarity and \Cluster algorithms. We might expect \Similarity to
achieve better quality at the same compression ratio since it updates the state
of the grammar between each variable replacement, on the other hand since it
must update the grammar it has the potential to run much more slowly than
\Cluster.

We don't report the running times for just \Sequitur since its linear running
time is negligible compared to our algorithms for all but the smallest input
data.

\subsubsection{Rep-n results}

In table \ref{simclus_r_t} we report the results on running \Sequitur and
\Cluster, without the grammar reductions, on the rep-n datasets. Time is the
wall clock running as measured on a 2.26 Ghz Intel Core 2 Duo Macbook Pro.
Ratio is the relative size of the grammar produced compared with \Sequitur,
where the size of the grammar is the sum of the lengths of the rhs's of the
rules. Levdistance is the levenshtein distance between the output of the
lossified grammar and the original input string, it is a kind of measure of the
fidelity of our algorithms but doesn't take into account how well patterns were
preserved. For the rep-n tests, proportion is the proportion of the final
string produced that was `*'. The closer to 1/30~0.033, the more accurate the
lossifier was in recreating the original texture of the input.

The columns of the data are prefixed by S or T depending on whether they are
measurements for \Similarity or \Cluster respectively.

The compression ratios achieved for both algorithms are roughly equal for the
same value for $\epsilon$, so it is fair to compare the algorithms for the same
$\epsilon$.

From plotting the data, we see that runtime of the algorithms are roughly
polynomial in the size of the data, so we can perform a linear regression on
the log-log transform of the data to find the exponents $\alpha$ for the
runtime $r(n)=n^\alpha$ where $n$ is the length of the input string. In the
chart below, all of the linear regressions had $R^2$ values of over $0.98$.

@@

For both values of $\epsilon$, The clustering algorithm is nearly linear, while
the similarity algorithm is roughly quadratic. On this dataset, the leveshtein
distances were similar for both algorithms but fairly high since the length of
the final string could change drastically.  The proportion of '*'s in the input
was usually the right order of magnitude, with both algorithms making big
mistakes occassionally. In most cases, the two algorithms maintained similarly
acceptable fidelity levels in recreating the texture of the original rep-n
input file.

The actual compression ratio was respectable, with both \Similarity and \Cluster
coming in at nearly half the size of the \Sequitur CFG.  Setting higher values
for $\epsilon$ had diminishing returns for compression for larger and larger
file sizes, at the cost of drastically lowering the fidelity of the output.

\subsubsection{Gen-n results}

Repeating the above tests on the \emph{gen-n} datasets yields the results in
table \ref{simclus_g_t}.

@@

Just as in the rep-n results, the two algorithms have almost identical
compression ratios and their fidelity is about the same both subjectively and
based on levenshtein distance. For an example of the text generated on one of
the gen-n datasets, see the appendix.

>>>>

It is useful to look at how the algorithms function on a small piece of data
with both plenty of hierarchical structure, and also some messiness that most
lossless compression schemes would not deal well with. As an example,
the string below is
similar to what one might come across in a math puzzle book.

@@

For most of our benchmark tests, we focused on two extreme kinds of data: one
with large amounts of repetition at all levels, and one with a word and
sentence level structure but with little obvious large-scale repetition.  One
set of test data was constructed by repeating the same letter `a' n-times but
then adding some texture to the data by changing 1/30 of the characters
uniformly at random to `*'. These are the \emph{rep-n} test-cases.
Another set of
test data was constructed from the first n characters of the book of Genesis
from the KJV version of the Bible. Call these test-cases \emph{gen-n}.

For our first suite of tests, we compare the effectiveness of the
\Similarity and \Cluster algorithms. We might expect \Similarity to
achieve better quality at the same compression ratio since it updates the state
of the grammar between each variable replacement, on the other hand since it
must update the grammar it has the potential to run much more slowly than
\Cluster. The running times for just \Sequitur aren't reported since its linear running
time is negligible compared to our algorithms.

In table \ref{simclus_r_t} we report the results on running \Sequitur and
\Cluster, without the grammar reductions, on the rep-n datasets. In table
\ref{simclus_g_t} we do the same for the gen-n datasets.
In these tests
we wanted to evaluate the relative fidelity, compression ratios, and runtime 
of the two algorithms.

In the table, Time is the
wall clock running as measured on a 2.26 Ghz Intel Core 2 Duo Macbook Pro.
Ratio is the relative size of the grammar produced compared with \Sequitur,
where the size of the grammar is the sum of the lengths of the rhs's of the
rules. Levdistance is the levenshtein distance between the output of the
lossified grammar and the original input string, it is a kind of measure of the
fidelity of our algorithms but doesn't take into account how well patterns were
preserved. For the rep-n tests, proportion is the proportion of the final
string produced that was `*'. The closer to 1/30~0.033, the more accurate the
lossifier was in recreating the original texture of the input.
The columns of the data are prefixed by S or T depending on whether they are
measurements for \Similarity or \Cluster respectively.

In both datasets, the 
compression ratios achieved for both algorithms are roughly equal given the
same value for $\epsilon$, so it is fair to compare the algorithms for the same
$\epsilon$. 
From plotting the data, we see that runtime of the algorithms are roughly
polynomial in the size of the data, so we can perform a linear regression on
the log-log transform of the data to find the exponents $\alpha$ for the
runtime $r(n)=n^\alpha$ where $n$ is the length of the input string. In the
chart below, all of the linear regressions had $R^2$ values of over $0.98$.

@@

For both values of $\epsilon$, The runtime for the
clustering algorithm is nearly linear, while
the similarity algorithm is roughly quadratic. On this dataset, the leveshtein
distances were similar for both algorithms but fairly high since the length of
the final string could change drastically.  The proportion of '*'s in the input
was usually the right order of magnitude, with both algorithms making big
mistakes occassionally. In most cases, the two algorithms maintained similarly
acceptable fidelity levels in recreating the texture of the original rep-n
input file.

As mentioned earlier,
the actual compression ratio was respectable, with both \Similarity and \Cluster
coming in at nearly half the size of the \Sequitur CFG. 
However, setting higher values
for $\epsilon$ had diminishing returns for compression for larger
file sizes, at the cost of drastically lowering the fidelity of the output.

@@

In line he two algorithms have almost identical
compression ratios and their fidelity is about the same both subjectively and
based on levenshtein distance. For an example of the text generated on one of
the gen-n datasets, see the appendix.
